Rapid cycleway prioritisation tool

### 2020-06-03 code/index.Rmd
Update description of three main layers

The maps contain five layers (two of which are hidden by default) that provide the results of our analysis, overlaying the basemaps.

Click on any of these layers to see a pop-up box containing more information about the road in question.

@@

This layer shows existing cycleways. This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure. This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps).

The following three layers are the central results of our analysis, representing the most promising locations for new cycleways.

## 3. Top routes

These are the 'top n' road sections in terms of cycling potential with 'spare space' defined above.
They may be suitable candidates for road space reallocation to create new cycleways. 
These roads have either a spare lane or width of at least 10m, and are ranked according to their mean cycling potential. 
For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the mean cycling potential multiplied by the length of the route. 
Top routes are listed in the table below the map, so you can see more information on them. 
The number of top routes selected is normally 20, with some variation by region.

We used certain eligibility criteria for the top routes:

@@

- The 'top routes' highlighted in the map-based results were produced automatically based on a simple score of continuous candidate road length multiplied by cycling potential. For roads with a length of more than 1 km, the cycling potential alone is used to rank roads. **The results should be interpreted based on local knowledge and an understanding of the limitations of the data. The results are designed to complement not replace other factors such as feedback from the local community and long-term strategic cycle network plans.**
- The estimates of cycling potential only include school and work travel. Accounting for increases in cycling for other trip purposes such as for shopping and leisure would increase cycling potential substantially.
- The results rely on grouping roads by proximity, name and other variables. Currently some roads that are strong candidates for new cycleways may be missing from the results because of how the algorithm works (we are working on this issue).
- The road network data was taken from the Cycling Infrastructure Prioritisation Toolkit (CyIPT) project which was completed in 2017, so may be out of date (we are looking at ways to update the data).
- The results are based on the existing road network and does not flag potential routes that could be constructed.

>>>>

The maps contain five layers (two of which are hidden by default) that provide the results of our analysis, overlaying the basemaps. 
Clicking on the lines on the map for any of these layers will reveal a pop-up box containing more information about the road or segment of interest.

The three main layers are arranged in order of planning timescales:

1. The **Existing cycleways** layer provides an approximation of where cycling infrastructure exists **in the recent past** and is intended to help identify gaps in the network that could be filled with new interventions.
2. The **Top ranked new cycleways** layer is the central result of the analysis, providing a list of roads that have high cycling potential, a minimum threshold length, and spare space according to our definition. These may be strong candidates for reallocation of road space **immediately or in the near future** to create new cycleways on strategic corridors under the first and second tranches of funding.
3. The **Cohesive network** layer is intended to show what a joined-up cycle network could look like, if road space was not a constraint on creating new infrastructure. Composed of roads that have high cycling potential on some or all of their length, the layer is designed to guide **long term planning** towards a continuous and coherent network.

These main layers, and two other layers that informed the results but which are not shown be default, are described in detail below.

@@

This layer shows existing cycleways. This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure. This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps).
The definition of 'cycleway' includes shared use paths but excludes cycle lanes painted on roads in this layer.

## 3. Top ranked new cycleways

These are the 'top n' road sections in terms of cycling potential with 'spare space' defined above.
They may be suitable candidates for road space reallocation to create new cycleways. 
These roads have either a spare lane or width of at least 10m, and are ranked according to their mean cycling potential. 
For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the mean cycling potential multiplied by the length of the route. 
Top ranked new cycleways are listed in the table below the map, so you can see more information on them. 
The number of Top ranked new cycleways selected is normally 20, with some variation by region.

We used certain eligibility criteria for the Top ranked new cycleways:

@@

- The 'Top ranked new cycleways' highlighted in the map-based results were produced automatically based on a simple score of continuous candidate road length multiplied by cycling potential. For roads with a length of more than 1 km, the cycling potential alone is used to rank roads. **The results should be interpreted based on local knowledge and an understanding of the limitations of the data. The results are designed to complement not replace other factors such as feedback from the local community and long-term strategic cycle network plans.**
- The estimates of cycling potential only include school and work travel. Accounting for increases in cycling for other trip purposes such as for shopping and leisure would increase cycling potential substantially.
- The results rely on grouping roads by proximity, name and other variables. Currently some roads that are strong candidates for new cycleways may be missing from the results because of how the algorithm works (we are working on this issue).
- The road network data was taken from the Cycling Infrastructure Prioritisation Toolkit (CyIPT) project which was completed in 2017, so may be out of date (we are looking at ways to update the data).
- The results are based on the existing road network and does not flag potential routes that could be constructed.
